How to compute the fusion product of MV cycles in type A

### 2021-05-17 draft.tex
qualms with L gamma

We begin with the following definitions.
\begin{definition}
Let $ L \subset \OO^m$ be a point in $ \Gr_+$.  We define the relative dimension of $L $ by
$$
\rdim L := \dim_\CC \OO^m/L\,. 
$$
% 
If $ \gamma \subset \{1, \dots, m\}$, we define two lattices $ L^\gamma, L_\gamma $ in $ \OO^\gamma := \Sp_{\OO}(e_i : i \in \gamma) $ by
\begin{gather*}
%    \OO^\gamma := \Sp_{\OO}(e_i : i \in \gamma) \\
L^\gamma:= L \cap \OO^\gamma  \qquad L_\gamma := L / L^{\gamma^c} \subset \OO^m / \OO^{\gamma^c} = \OO^\gamma
\end{gather*}
where $ \gamma^c := \{1, \dots, m \} \setminus \gamma$.
\end{definition}
We will also need the analogous definitions when $ \OO$ is replaced by $ \CC[t]$ and $L \in \Grth_+$.

@@

We can associate to $\tau$ an MV cycle as follows. Let    
%  
\begin{equation*}
    \mathring Z(\tau) = 
        \{
            L\in S^\mu : L_{\{1, \dots, i\}} \in\Gr^{\lambda(i)}\text{ for } i = 1, \dots m 
        \}
\end{equation*}
and $Z(\tau) = \overline{\mathring Z(\tau)}$. 
% 
\jcom{Maybe use $ [m] $ for $\{1, \dots, m\}$ ?}

@@

First, we consider
\begin{equation*}
Z(\tau)_1 := \{ L \in S^\mu \cap \Gr_+ : L_{\{1, \dots, i\}} \in S_+^{\lambda(i)} \text{ for } i = 1, \dots m\} \,. 
%Z(\tau)_2 := \{ L \in S^\mu : L \cap \cO^i \in S^{\lambda(i)} \cap \Gr^{\lambda(i)} \text{ for } i = 1, \dots m\}
\end{equation*}

@@

\jcom{We could write that $ \lambda(i)_j + \dots + \lambda(i)_i$ is the number of boxes on rows $ j, \dots, i$ filled with $ 1, \dots, i $.}

From  the proof of \cite[Proposition 9.6]{kamnitzer2010mirkovic}, we see that $ Z(\tau)_1$ is equal to $ t^\mu A(n_\bullet(\tau))$, where $ A(n_\bullet)$ is defined in section 4.3 of \cite{kamnitzer2010mirkovic}.  Thus, $ \overline{Z(\tau_1)}$ is the MV cycle whose Lusztig datum is $ n_\bullet(\tau) $. (In \cite{kamnitzer2010mirkovic}, we worked with $  G(\OO) \backslash G(\cK)$, which we identify with $ \Gr $ using $ [g] \mapsto [g^{-1}]$.)

>>>>

We begin with the following definitions.
\begin{definition}
Let $ L \subset \OO^m$ be a point in $ \Gr_+$.  We define the relative dimension of $L $ by
$$
\rdim L := \dim_\CC \OO^m/L\,. 
$$
% 
If $ \gamma \subset \{1, \dots, m\}$, we define two lattices $ L^\gamma, L_\gamma $ in $ \OO^\gamma := \Sp_{\OO}(e_i : i \in \gamma) $ by
\begin{gather*}
%    \OO^\gamma := \Sp_{\OO}(e_i : i \in \gamma) \\
L^\gamma:= L \cap \OO^\gamma  \qquad L_\gamma := L / L^{\gamma^c} \subset \OO^m / \OO^{\gamma^c} = \OO^\gamma
\end{gather*}
where $ \gamma^c := \{1, \dots, m \} \setminus \gamma$.
\acom{I suggest replacing $\mathbb O$ by $R$, and $L/L^{\gamma^c}$ by $(L + R^{\gamma^c})/R^{\gamma^c}$ because that's what we're doing. In a lower triangular $g(A)$ columns ${i+1..m}$ cannot be used to eliminate entries in rows ${i+1..m}$ in the first $i$ columns over $\CC[t]$ or $\CC\xt$.}
\end{definition}
We will also need the analogous definitions when $ \OO$ is replaced by $ \CC[t]$ and $L \in \Grth_+$.

@@

We can associate to $\tau$ an MV cycle as follows. Let    
%  
\begin{equation*}
    \mathring Z(\tau) = 
        \{
            L\in S^\mu : L_{\{1, \dots, i\}} \in\Gr^{\lambda(i)}\text{ for } i = 1, \dots m 
        \}
\end{equation*}
and $Z(\tau) = \overline{\mathring Z(\tau)}$. 
% 
\jcom{Maybe use $ [m] $ for $\{1, \dots, m\}$ ?}
\acom{And $\{1,\dots,i\}$ etc.}

@@

First, we consider \acom{add \texttt{mathring}'s to these $Z$'s?}
\begin{equation*}
Z(\tau)_1 := \{ L \in S^\mu \cap \Gr_+ : L_{\{1, \dots, i\}} \in S_+^{\lambda(i)} \text{ for } i = 1, \dots m\} \,. 
%Z(\tau)_2 := \{ L \in S^\mu : L \cap \cO^i \in S^{\lambda(i)} \cap \Gr^{\lambda(i)} \text{ for } i = 1, \dots m\}
\end{equation*}

@@

\jcom{We could write that $ \lambda(i)_j + \dots + \lambda(i)_i$ is the number of boxes on rows $ j, \dots, i$ filled with $ 1, \dots, i $.}
\acom{\emoji{thumbsup}}

From  the proof of \cite[Proposition 9.6]{kamnitzer2010mirkovic}, we see that $ Z(\tau)_1$ is equal to $ t^\mu A(n_\bullet(\tau))$, where $ A(n_\bullet)$ is defined in section 4.3 of \cite{kamnitzer2010mirkovic}.  Thus, $ \overline{Z(\tau_1)}$ is the MV cycle whose Lusztig datum is $ n_\bullet(\tau) $. (In \cite{kamnitzer2010mirkovic}, we worked with $  G(\cO) \backslash G(\cK)$, which we identify with $ \Gr $ using $ [g] \mapsto [g^{-1}]$.)
